Estimating contemporary migration numbers of adults for iteroparous species using kinship pairs found between populations

### 2022-02-07 latex/ms.tex
write 4th  para in Intro, #15

Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the information about kinship in a sample, owing to the recent advances in genetic methods for kinship determination \cite[]{https://doi.org/10.1111/faf.12615}.

This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}. Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method. Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect $N$. While the original CKMR is designed to estimate adult abundance (i.e., $N$), the monitoring data for CKMR also produce the estimator of $N_{\rm e}$ by detecting half-sibling (HS) pairs within the same cohort \cite[]{Akita_2019}. This kinship-oriented estimation of $N_{\rm e}$ was presented in the context of the sibship assignment method \cite[]{wang2009new} and is expected to provide a much more accurate estimator as kinship determination becomes more accurate.

@@

%  (e.g., \cite{Hastings_1993} numerically demonstrates that two populations become demographically independent when migration rate $< 0.1$)
% withinのデータはどう使う？？
%PRE-DEFINED population !
%Caveat: selectivity, family correlated migration、skip spawning,

>>>>

Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the information about kinship in a sample, owing to the recent advances in genetic methods for kinship determination \cite[recently reviewed in][]{https://doi.org/10.1111/faf.12615}. The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method. Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect an adult number in the population \cite[]{bravington2016close}. While recent studies of CKMR argued that availability of kinship information for applying estimation of migration rate \cite[]{https://doi.org/10.1002/ece3.6296, 10.1093/icesjms/fsac002}

% 最近のConnの研究では、明示的に集団構造をCKMRの枠組みでキャプチャーしようとする枠組みについて議論されているが、その明示的な取り扱いやシミュレーションについては研究されていない。

%This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}. Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method. Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect $N$. While the original CKMR is designed to estimate adult abundance (i.e., $N$), the monitoring data for CKMR also produce the estimator of $N_{\rm e}$ by detecting half-sibling (HS) pairs within the same cohort \cite[]{Akita_2019}. This kinship-oriented estimation of $N_{\rm e}$ was presented in the context of the sibship assignment method \cite[]{wang2009new} and is expected to provide a much more accurate estimator as kinship determination becomes more accurate.

@@

%  (e.g., \cite{Hastings_1993} numerically demonstrates that two populations become demographically independent when migration rate $< 0.1$)
% withinのデータはどう使う？？withinとbetweenを比較して、betweenが優位に少ないかどうかなどが構造発見につながるかもconn et al 2020 EcolEvolもチェック
%PRE-DEFINED population !
%Caveat: selectivity, family correlated migration、skip spawning,
